---
title: "Assigment - kNN DIY"
author:
- Vy Nguyen - Author
- Koko Nguyuen - Reviewer
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: '2'
    df_print: paged
  html_notebook:
    toc: yes
    toc_depth: 2
---


```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

---
## Business Understanding


## Data Understanding
Three data sets are submitted, for training and testing. Ground-truth occupancy was obtained from time stamped pictures that were taken every minute.

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-occupancy.csv"
rawDS <- read_csv(url)
str(rawDS)
```
The dataset has 7 variables (columns) and 8143 observations (rows)

## Data Preparation
The first variable, "date", contains unique time.The date do not contain any relevant information for making predictions, so will delete it from the data set

```{r}
cleanDS <- rawDS[-1]
head(cleanDS)
```
The variable named occupancy contains the outcomes we would like to predict - '0' for 'not occupied', '1' for 'occupied status.'

The variable we would like to predict is called the 'occupancy'. We can look at the counts and proportions for both outcomes, using the table() and prop.tables() functions. 

```{r}
cntDiag <- table(cleanDS$Occupancy)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)
cntDiag
```

```{r}
propDiag
```

The variable is now coded as a type character. Many models require that the label is of type factor. This is easily solved using factor() function.
```{r}
cleanDS$Occupancy <- factor(cleanDS$Occupancy, levels = c("1", "0"), labels = c("occupied status", "not occupied")) %>% relevel("not occupied")
head(cleanDS, 10)
```
```{r}
summary(cleanDS[c("Temperature", "Humidity", "Light", "CO2")])
```

```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}

testSet1 <- c(1:4)
testSet2 <- c(1:4) * 10

cat("testSet1:", testSet1, "\n")
```

```{r}
cat("testSet2:", testSet2, "\n")
```

```{r}
cat("Normalized testSet1:", normalize(testSet1), "\n")
```

```{r}
cat("Normalized testSet2:", normalize(testSet2))
```

```{r}
cleanDS_n <- sapply(1:5,
                    function(x) {
  normalize(cleanDS[,x])
}) %>% as.data.frame()

summary(cleanDS_n[c("Temperature", "Humidity", "Light", "CO2")])
```

```{r}
trainDS_feat <- cleanDS_n[1:469,  ]
testDS_feat <- cleanDS_n[470:8143,  ]
```

```{r}
trainDS_labels <- cleanDS[1:469,  1]
testDS_labels <- cleanDS[470:8143,  1]
```

## Modeling
```{r}
cleanDS_test_pred <- knn(train = as.matrix(trainDS_feat), test = as.matrix(testDS_feat), cl = as.matrix(trainDS_labels), k = 21)
head(cleanDS_test_pred)
```

```{r}

```

## Evaluation and Deployment
text and code here

## Reviewer adds suggestions for improving the model
- While splitting data to test set and train set, you chose the wrong range. SHould be extended to 8143
-While doing the test and train set you chose the wrong number of variables
- Try splitting data in testing & training set step to a different size (ex:50/50) for a better accuracy